Domain-specific working memory loads selectively increase negative interpertations of surprised facial expressions

### 2019-08-07 Manuscript/Manuscript.Rmd
Updated manuscript, updated cleaning
Removing ridiculous variable creation in the cleaning script. Implementing "which" statements.

Manuscript runs, but is still messy.

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
### import z score updated function ###
source("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/wilcox_test.R")
### code edits taken from : https://stats.stackexchange.com/questions/306841/z-score-on-wilcoxon-signed-ranks-test ###

### load necessary libraries ###
library(readxl)
library(tidyverse)
library(openxlsx)
library(Rmisc)
library(broom)
```
# Introduction
Facial expressions are rich with affective information, and correctly interpreting these social cues is critical for successfully navigating the social world. In fact, facial expressions are seen across cultures [@ekman_constants_1971] and some evidence suggests expressions are innate (cite). Often, facial expressions serve as a clear social signal, but this is not always the case. While a smile from a friend likely expresses a positive affective state, other cues are not so clear. For instance, a surprised facial expression could signal either a positive (e.g., winning the lottery) or negative (e.g., a snake in the woods) affective state. In the absence of a larger context, individuals differ in their tendency to interpret surprised facial expressions as either positive or negative. Importantly, this affective bias extends beyond facial expressions, as individuals often show a similar bias to both surprised faces and ambiguous scenes [@neta_neural_2013]. This bias towards positive or negative interpretations is known as one's valence bias. 
Interpreting facial expressions requires both bottom-up (e.g., perceptual input) and top-down (e.g., emotion regulation strategies) processes. A growing body of work suggests that the initial interpretation of emotionally ambiguous stimuli is negative and driven by bottom-up processes, and that arriving at a positive interpretation requires additional, top-down regulatory processes. For example, participants reliably rate surprise as negative faster than positive [@neta_dont_2016]. In fact, forcing participants to slow their responding during interpretations of ambiguous images shifts individuals' biases towards positivity [@neta_its_2018]. Perceptual input also contributes to valence bias. In one recent study, Neta and colleagues [-@neta_all_2017] showed that faster intial fixation, as well as longer overall fixation, on the mouth is related to more positive interpretations of surprised faces and that forcing gaze patterns to match those of modulated interpretations of surprised expressions. In short,  
Despite the trait-like nature of this bias [@neta_corrugator_2009], valence bias may be shifted, at least temporarily, by a number of experimental manipulations. As mentioned above, simple manipulations like slowing response times will shift bias [@neta_its_2018]. Additional work has shown that increases in salivary cortisol after a stressor relate to more negative interpretations of surprised faces from baseline to post-stressor [@brown_cortisol_2017]. Similarly, participants with positive biases at baseline will interpret surprise as more negative under threat of shock [@neta_impact_2017], suggesting that taxing cognitive resources, in this case attention, reduces the ability of individuals to interpret surprised faces as positive.

@@

## Material
### Stimuli
``` {r stimulus_t.test, include = FALSE}
stim.data <- read.xlsx("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/IAPS_Stim_List.xlsx")
shapiro.test(subset(stim.data, Condition == "POS")$Aro_Mn)
shapiro.test(subset(stim.data, Condition == "NEG")$Aro_Mn)
stim.t.test <- wilcox_test(subset(stim.data, Condition == "POS")$Aro_Mn, subset(stim.data, Condition == "NEG")$Aro_Mn)
```
The stimuli included faces taken from the NimStim [@tottenham_nimstim_2009] and Karolinska Directed Emotional Faces [@lundqvist_karolinska_1998] stimuli sets. The faces consisted of 34 unique identities including 11 angry, 12 happy, and 24 surprised expressions organized pseudorandomly. The scenes were taken from the International Affective Picture System [@lang_international_2008]. A total of 288 scenes (72 positive, 72 negative, and 144 neutral) were selected for the image matrices. The positive and negative images did not differ on arousal (Z = `r printnum(stim.t.test$z_val)`, p = `r printnum(stim.t.test$p.value)`). The scenes were organized into low (two images) and high (six images) cognitive load of either neutral or emotional (equal number of positive and negative) images (Figure 1).

@@

# Results
## Subjective ratings
```{r import data and analyze ratings, include = FALSE, echo = TRUE}
data <- read.csv("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/Final.Data.csv_2019-08-01_12-38-57.csv")
### remove psych disorders ### Ask maital?
# data <- data[-c(4, 33, 37, 38, 41, 47),]

### assess normality ###
shapiro.test(data$lo.neu.sur_rate)
shapiro.test(data$hi.neu.sur_rate)
shapiro.test(data$lo.emo.sur_rate)
shapiro.test(data$hi.emo.sur_rate)

@@

## Reaction times
```{r analyze RTs, include = FALSE}
## assess normality ###
 shapiro.test(data$lo.neu.sur_RTz)
 shapiro.test(data$hi.neu.sur_RT)
 shapiro.test(data$lo.emo.sur_RT)
 shapiro.test(data$hi.emo.sur_RT)

### force normality ###
RTz.long <- gather(data, key = Condition, value = RTz,
                   lo.neu.sur_RT,
                   hi.neu.sur_RT,
                   lo.emo.sur_RT,
                   hi.emo.sur_RT)

RTz.long$RTz <- ave(RTz.long$RTz, RTz.long$subjID, FUN=scale)

wide <- spread(RTz.long, key = Condition, value = RTz)
shapiro.test(wide$lo.emo.sur_RT)
### make factors ###
RTz.long$Load <- ifelse(RTz.long$Condition == "lo.neu.sur_RT", "Low",
                         ifelse(RTz.long$Condition == "lo.emo.sur_RT", "Low",
                                ifelse(RTz.long$Condition == "hi.neu.sur_RT", "High",
                                       ifelse(RTz.long$Condition == "hi.emo.sur_RT", "High", ""))))

RTz.long$Type <- ifelse(RTz.long$Condition == "lo.neu.sur_RT", "Neutral",
                         ifelse(RTz.long$Condition == "lo.emo.sur_RT", "Emotional",
                                ifelse(RTz.long$Condition == "hi.neu.sur_RT", "Neutral",
                                       ifelse(RTz.long$Condition == "hi.emo.sur_RT", "Emotional", ""))))

@@

```
To assses for normality, the data were first tested with Shapiro-Wilk's test. All conditions appeared to be sampled from normal distributions (p's > .08). A Load (Low, High) X Type (Neutral, Emotional) repeated measures ANOVA was used to assess differences in the RTs. There was a trend towards a main effect of type, F(`r (RTaov$df[which(RTaov$term == "Type")])`, `r (RTaov$df[which(RTaov$stratum == "subjID")])`) = `r printnum(RTaov$statistic[which(RTaov$term == "Type")])`, p = `r printnum(RTaov$p.value[which(RTaov$term == "Type")])`. However, follow up Wilcoxon signed rank tests did not reveal any differences that survived correction for multiple comparisons. There was a trend for RTs of face ratings on high load emotional trials to be longer than high load neutral trials (p =), and a similar pattern for low load emotional trial ratings to take longer than high load neutral trials (p = . One other comparison approached trend levels of signficance, with low load neutral trial ratings taking longer than high neutral loads, (p = . All other comparisons were non-significant (p's > .

```{r plot RT data}
#data.long.summary <- summarySE(data.long, measurevar="ReactionTime", groupvars = "Condition")
#ggplot(data.long.summary, aes(Condition, `ReactionTime`, fill = as.factor(Condition))) +
 # geom_bar(stat = "summary", fun.y = "mean") +
#  geom_errorbar(aes(ymin=`ReactionTime`-se, ymax=`ReactionTime`+se), width=.1)
```

``` {r RT by ratings, include = TRUE}
# ### assess for normality ###
# shapiro.test(data$lo.neu.sur_n_RT) ## non-normal
# shapiro.test(data$lo.neu.sur_p_RT) ## normal
# shapiro.test(data$hi.neu.sur_n_RT) ## non-normal
# shapiro.test(data$hi.neu.sur_p_RT) ## normal
# shapiro.test(data$lo.emo.sur_n_RT) ## non-normal
# shapiro.test(data$lo.emo.sur_p_RT) ## non-normal
# shapiro.test(data$hi.emo.sur_n_RT) ## barely normal
# shapiro.test(data$hi.emo.sur_p_RT) ## non-normal
# 
# ### t-test for pos ratings vs. neg ratings
# lo.neu.RT.pvn <- wilcox.test(data$lo.neu.sur_n_RT, data$lo.neu.sur_p_RT, paired = TRUE)
# wilcox.test(data$hi.neu.sur_n_RT, data$hi.neu.sur_p_RT, paired = TRUE)
# wilcox.test(data$lo.emo.sur_n_RT, data$lo.emo.sur_p_RT, paired = TRUE)
# wilcox.test(data$hi.emo.sur_n_RT, data$hi.emo.sur_p_RT, paired = TRUE)
# 
# ### make long ###
# data.long <- gather(data, key = "Condition", value = "ReactionTime",
#                     lo.neu.sur_n_RT, hi.neu.sur_n_RT,
#                     lo.emo.sur_n_RT, hi.emo.sur_n_RT,
#                     lo.neu.sur_p_RT, hi.neu.sur_p_RT,
#                     lo.emo.sur_p_RT, hi.emo.sur_p_RT)
# data.long$Condition <- as.factor(data.long$Condition)
# 
# data.long.summary <- summarySE(data.long, measurevar="ReactionTime", groupvars="Condition", na.rm = TRUE)
# 
# ggplot(data.long.summary, aes(Condition, ReactionTime, fill = as.factor(Condition))) +
#   geom_bar(stat = "summary", fun.y = "mean", na.rm = TRUE) +
#   geom_errorbar(aes(ymin=ReactionTime-se, ymax=ReactionTime+se), width=.1)

### force normality ###
RTz.long <- gather(data, key = Condition, value = RTz,
                   lo.neu.sur_n_RT, lo.neu.sur_p_RT,
                   hi.neu.sur_n_RT, hi.neu.sur_p_RT,
                   lo.emo.sur_n_RT, lo.emo.sur_p_RT,
                   hi.emo.sur_n_RT, hi.emo.sur_p_RT)

RTz.long$RTz <- ave(RTz.long$RTz, RTz.long$subjID, FUN=scale)

### back to wide ###
data2 <- spread(RTz.long, key = Condition, value = RTz)
### assess for normality ###
shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "lo.neu.sur_n_RT")])
shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "lo.neu.sur_p_RT")])
shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "hi.neu.sur_n_RT")])
shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "hi.neu.sur_p_RT")])
shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "lo.emo.sur_n_RT")])
shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "lo.emo.sur_p_RT")])
shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "hi.emo.sur_n_RT")])
shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "hi.emo.sur_p_RT")])

RTz.long$Condition <- as.factor(RTz.long$Condition)

### make factors ###
RTz.long$Load <- ifelse(RTz.long$Condition == "lo.neu.sur_n_RT", "Low",
                         ifelse(RTz.long$Condition == "lo.emo.sur_RT", "Low",
                                ifelse(RTz.long$Condition == "hi.neu.sur_RT", "High",
                                       ifelse(RTz.long$Condition == "hi.emo.sur_RT", "High", ""))))

RTz.long$Type <- ifelse(RTz.long$Condition == "lo.neu.sur_RT", "Neutral",
                         ifelse(RTz.long$Condition == "lo.emo.sur_RT", "Emotional",
                                ifelse(RTz.long$Condition == "hi.neu.sur_RT", "Neutral",
                                       ifelse(RTz.long$Condition == "hi.emo.sur_RT", "Emotional", ""))))

### make w/in subjs factors ###
data.long$subjID <- as.factor(data.long$subjID)

### traditional ANOVA ###
RTaov <- with(data.long,
                   aov(ReactionTime ~ (Load * Type) +
                       Error(subjID / (Load * Type))), contrasts = contr.sum())
summary(RTaov)
RTaov <- tidy(RTaov)

@@

@@

``` {r MAD}
###  MAD analyses ###
results.long <- gather(data, key = "Condition", value = "MAD",
                       lo.emo.sur_MAD, hi.emo.sur_MAD, lo.neu.sur_MAD, hi.neu.sur_MAD)
results.long$load <- ifelse(results.long$Condition == "lo.emo.sur_MAD", "Low",
                            ifelse(results.long$Condition == "lo.neu.sur_MAD", "Low", "High"))
results.long$type <- ifelse(results.long$Condition == "lo.emo.sur_MAD", "Emo",
                            ifelse(results.long$Condition == "hi.emo.sur_MAD", "Emo", "Neu"))

@@

res.long.sum <- summarySE(results.long, measurevar="MAD", groupvars = "Condition")
ggplot(res.long.sum, aes(Condition, MAD, fill = as.factor(Condition))) +
  geom_bar(stat = "summary", fun.y = "mean") +
  geom_errorbar(aes(ymin=`MAD`-se, ymax=`MAD`+se), width=.1)

```

>>>>

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
### import z score updated function ###
source("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/wilcox_test.R")
### code edits taken from : https://stats.stackexchange.com/questions/306841/z-score-on-wilcoxon-signed-ranks-test ###

### load necessary libraries ###
suppressPackageStartupMessages(library(readxl)) 
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(openxlsx))
suppressPackageStartupMessages(library(Rmisc))
suppressPackageStartupMessages(library(broom))
```
# Introduction
Facial expressions are rich with affective information, and correctly interpreting these social cues is critical for successfully navigating the social world. In fact, facial expressions are seen across cultures [@ekman_constants_1971] and some evidence suggests expressions are innate (cite). Often, facial expressions serve as a clear social signal, but this is not always the case. While a smile from a friend likely expresses a positive affective state, other cues are not so clear. For instance, a surprised facial expression could signal either a positive (e.g., winning the lottery) or negative (e.g., a snake in the woods) affective state. In the absence of a larger context, individuals differ in their tendency to interpret surprised facial expressions as either positive or negative. Importantly, this affective bias extends beyond facial expressions, as individuals often show a similar bias to both surprised faces and ambiguous scenes [@neta_neural_2013]. This bias towards positive or negative interpretations is known as one's valence bias. 
Interpreting facial expressions requires both bottom-up (e.g., perceptual input) and top-down (e.g., emotion regulation strategies) processes. A growing body of work suggests that the initial interpretation of emotionally ambiguous stimuli is negative and driven by bottom-up processes, and that arriving at a positive interpretation requires additional, top-down regulatory processes. For example, participants reliably rate surprise as negative faster than positive [@neta_dont_2016]. In fact, forcing participants to slow their responding during interpretations of ambiguous images shifts individuals' biases towards positivity [@neta_its_2018]. Perceptual input also contributes to valence bias. In one recent study, Neta and colleagues [-@neta_all_2017] showed that faster intial fixation, as well as longer overall fixation, on the mouth is related to more positive interpretations of surprised faces and that forcing gaze patterns to match those of modulated interpretations of surprised expressions. In short,  
Despite the trait-like nature of this bias [@neta_corrugator_2009], valence bias may be shifted, at least temporarily, by a number of experimental manipulations. As mentioned above, simple manipulations like slowing response times will shift bias [@neta_its_2018]. Additional work has shown that increases in salivary cortisol after a stressor relate to more negative interpretations of surprised faces from baseline to post-stressor [@brown_cortisol_2017]. Similarly, participants with positive biases at baseline will interpret surprise as more negative under threat of shock [@neta_impact_2017], suggesting that taxing cognitive resources, in this case attention, reduces the ability of individuals to interpret surprised faces as positive.

@@

## Material
### Stimuli
``` {r stimulus_t.test, include = FALSE}
stim.data <- read.xlsx("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/IAPS_Stim_List.xlsx")
shapiro.test(subset(stim.data, Condition == "POS")$Aro_Mn)
shapiro.test(subset(stim.data, Condition == "NEG")$Aro_Mn)
stim.t.test <- wilcox_test(subset(stim.data, Condition == "POS")$Aro_Mn, subset(stim.data, Condition == "NEG")$Aro_Mn)
```
The stimuli included faces taken from the NimStim [@tottenham_nimstim_2009] and Karolinska Directed Emotional Faces [@lundqvist_karolinska_1998] stimuli sets. The faces consisted of 34 unique identities including 11 angry, 12 happy, and 24 surprised expressions organized pseudorandomly. The scenes were taken from the International Affective Picture System [@lang_international_2008]. A total of 288 scenes (72 positive, 72 negative, and 144 neutral) were selected for the image matrices. The positive and negative images did not differ on arousal (Z = `r printnum(stim.t.test$z_val)`, p = `r printnum(stim.t.test$p.value)`). The scenes were organized into low (two images) and high (six images) cognitive load of either neutral or emotional (equal number of positive and negative) images (Figure 1).

@@

# Results
## Subjective ratings
```{r import data and analyze ratings, include = FALSE, echo = TRUE}
data <- read.csv("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/Data/Cleaned_Data/Final.Data.csv_2019-08-01_12-38-57.csv")
### remove psych disorders ### Ask maital?
# data <- data[-c(4, 33, 37, 38, 41, 47),]

### assess normality ###
shapiro.test(data$lo.neu.sur_rate) # non-normal
shapiro.test(data$hi.neu.sur_rate) # non-normal
shapiro.test(data$lo.emo.sur_rate) # non-normal
shapiro.test(data$hi.emo.sur_rate) # non-normal

@@

## Reaction times
```{r analyze RTs, include = FALSE}
## assess normality ###
shapiro.test(data$lo.neu.sur_RTz)
shapiro.test(data$hi.neu.sur_RTz)
shapiro.test(data$lo.emo.sur_RTz)
shapiro.test(data$hi.emo.sur_RTz)

### force normality ###
RTz.long <- gather(data, key = Condition, value = RTz,
                   lo.neu.sur_RTz,
                   hi.neu.sur_RTz,
                   lo.emo.sur_RTz,
                   hi.emo.sur_RTz)

### run Friedman's test and store results ###
RTz.friedman <- friedman.test(RTz ~ Condition|subjID, data = RTz.long)
lo.emo.v.lo.neu.RTz <- wilcox_test(data$lo.emo.sur_RTz, data$lo.neu.sur_RTz, paired = TRUE, conf.int = TRUE)
lo.emo.v.hi.neu.RTz <- wilcox_test(data$lo.emo.sur_RTz, data$hi.neu.sur_RTz, paired = TRUE, conf.int = TRUE)
lo.emo.v.hi.emo.RTz <- wilcox_test(data$lo.emo.sur_RTz, data$hi.emo.sur_RTz, paired = TRUE, conf.int = TRUE)
hi.emo.v.lo.neu.RTz <- wilcox_test(data$hi.emo.sur_RTz, data$lo.neu.sur_RTz, paired = TRUE, conf.int = TRUE)
hi.emo.v.hi.neu.RTz <- wilcox_test(data$hi.emo.sur_RTz, data$hi.neu.sur_RTz, paired = TRUE, conf.int = TRUE)
lo.neu.v.hi.neu.RTz <- wilcox_test(data$hi.neu.sur_RTz, data$lo.neu.sur_RTz, paired = TRUE, conf.int = TRUE)

# RTz.long$RTz <- ave(RTz.long$RTz, RTz.long$subjID, FUN=scale)

# wide <- spread(RTz.long, key = Condition, value = RTz)
# hapiro.test(wide$lo.emo.sur_RT)
### make factors ###
RTz.long$Load <- ifelse(RTz.long$Condition == "lo.neu.sur_RTz", "Low",
                         ifelse(RTz.long$Condition == "lo.emo.sur_RTz", "Low",
                                ifelse(RTz.long$Condition == "hi.neu.sur_RTz", "High",
                                       ifelse(RTz.long$Condition == "hi.emo.sur_RTz", "High", ""))))

RTz.long$Type <- ifelse(RTz.long$Condition == "lo.neu.sur_RTz", "Neutral",
                         ifelse(RTz.long$Condition == "lo.emo.sur_RTz", "Emotional",
                                ifelse(RTz.long$Condition == "hi.neu.sur_RTz", "Neutral",
                                       ifelse(RTz.long$Condition == "hi.emo.sur_RTz", "Emotional", ""))))

@@

```
To assess for normality, the data were first tested with Shapiro-Wilk's test. Two conditions did not appear to be sampled from normal distributions, so non-parametric tests were used. Overall, there was a trending difference across the four conditions, $\chi^{2}$(`r (printnum(RTz.friedman$parameter))`) = `r printnum(RTz.friedman$statistic)`, p `r printp(RTz.friedman$p.value)`. Wilcoxon signed rank tests were used to assess post-hoc comparisons and Bonferroni corrected p-value = `r printnum(.05 / 6)`. While none of the post-hoc comparisons reached the adjusted significance level, there was a trending difference between emotional and neutral RTs in the high load condition, Z = `r printnum(hi.emo.v.hi.neu.RTz$z_val)`, p = `r printp(hi.emo.v.hi.neu.RTz$p.value)`, such that high emotional WM loads had slower RTs. Two other comparisons were trending for traditional levels of significance. Low emotional WM loads tended to take marginally longer than high neutral WM loads, Z = `r printnum(lo.emo.v.hi.neu.RTz$z_val)`, p = `r printp(lo.emo.v.hi.neu.RTz$p.value)`, and low neutral WM loads took marginally longer than high neutral WM laods, Z = `r printnum(lo.neu.v.hi.neu.RTz$z_val)`, p = `r printnum(lo.neu.v.hi.neu.RTz$p.value)`. All other comparisons were not significant.
<!-- IF WE USE RAW RTS, USE THIS TEXT
To assses for normality, the data were first tested with Shapiro-Wilk's test. All conditions appeared to be sampled from normal distributions (p's > .08). A Load (Low, High) X Type (Neutral, Emotional) repeated measures ANOVA was used to assess differences in the RTs. There was a trend towards a main effect of type, F(`r (RTaov$df[which(RTaov$term == "Type")])`, `r (RTaov$df[which(RTaov$stratum == "subjID")])`) = `r printnum(RTaov$statistic[which(RTaov$term == "Type")])`, p = `r printnum(RTaov$p.value[which(RTaov$term == "Type")])`. However, follow up Wilcoxon signed rank tests did not reveal any differences that survived correction for multiple comparisons. There was a trend for RTs of face ratings on high load emotional trials to be longer than high load neutral trials (p =), and a similar pattern for low load emotional trial ratings to take longer than high load neutral trials (p = . One other comparison approached trend levels of signficance, with low load neutral trial ratings taking longer than high neutral loads, (p = . All other comparisons were non-significant (p's > .
-->

```{r plot RT data, include = TRUE}
ggplot(RTz.long, aes(Condition, `RTz`, fill = as.factor(Condition))) +
  geom_bar(stat = "summary", fun.y = "mean") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1)
```

``` {r RT by ratings, include = FALSE}
### assess for normality ###
shapiro.test(data$lo.neu.sur_n_RT) ## non-normal
shapiro.test(data$lo.neu.sur_p_RT) ## normal
shapiro.test(data$hi.neu.sur_n_RT) ## non-normal
shapiro.test(data$hi.neu.sur_p_RT) ## normal
shapiro.test(data$lo.emo.sur_n_RT) ## non-normal
shapiro.test(data$lo.emo.sur_p_RT) ## non-normal
shapiro.test(data$hi.emo.sur_n_RT) ## barely normal
shapiro.test(data$hi.emo.sur_p_RT) ## non-normal

### t-test for pos ratings vs. neg ratings
lo.neu.RT.pvn <- wilcox.test(data$lo.neu.sur_n_RT, data$lo.neu.sur_p_RT, paired = TRUE)
wilcox.test(data$hi.neu.sur_n_RT, data$hi.neu.sur_p_RT, paired = TRUE)
wilcox.test(data$lo.emo.sur_n_RT, data$lo.emo.sur_p_RT, paired = TRUE)
wilcox.test(data$hi.emo.sur_n_RT, data$hi.emo.sur_p_RT, paired = TRUE)

### make long ###
data.long <- gather(data, key = "Condition", value = "ReactionTime",
                    lo.neu.sur_n_RT, hi.neu.sur_n_RT,
                    lo.emo.sur_n_RT, hi.emo.sur_n_RT,
                    lo.neu.sur_p_RT, hi.neu.sur_p_RT,
                    lo.emo.sur_p_RT, hi.emo.sur_p_RT)
data.long$Condition <- as.factor(data.long$Condition)

@@

# ### force normality ###
# RTz.long <- gather(data, key = Condition, value = RTz,
#                    lo.neu.sur_n_RT, lo.neu.sur_p_RT,
#                    hi.neu.sur_n_RT, hi.neu.sur_p_RT,
#                    lo.emo.sur_n_RT, lo.emo.sur_p_RT,
#                    hi.emo.sur_n_RT, hi.emo.sur_p_RT)
# 
# ### back to wide ###
# data2 <- spread(RTz.long, key = Condition, value = RTz)
# ### assess for normality ###
# shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "lo.neu.sur_n_RT")])
# shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "lo.neu.sur_p_RT")])
# shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "hi.neu.sur_n_RT")])
# shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "hi.neu.sur_p_RT")])
# shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "lo.emo.sur_n_RT")])
# shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "lo.emo.sur_p_RT")])
# shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "hi.emo.sur_n_RT")])
# shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "hi.emo.sur_p_RT")])
# 
# RTz.long$Condition <- as.factor(RTz.long$Condition)
# 
# ### make factors ###
# RTz.long$Load <- ifelse(RTz.long$Condition == "lo.neu.sur_n_RT", "Low",
#                          ifelse(RTz.long$Condition == "lo.emo.sur_RT", "Low",
#                                 ifelse(RTz.long$Condition == "hi.neu.sur_RT", "High",
#                                        ifelse(RTz.long$Condition == "hi.emo.sur_RT", "High", ""))))
# 
# RTz.long$Type <- ifelse(RTz.long$Condition == "lo.neu.sur_RT", "Neutral",
#                          ifelse(RTz.long$Condition == "lo.emo.sur_RT", "Emotional",
#                                 ifelse(RTz.long$Condition == "hi.neu.sur_RT", "Neutral",
#                                        ifelse(RTz.long$Condition == "hi.emo.sur_RT", "Emotional", ""))))
# 
# ### make w/in subjs factors ###
# data.long$subjID <- as.factor(data.long$subjID)
# 
# ### traditional ANOVA ###
# RTaov <- with(data.long,
#                    aov(ReactionTime ~ (Load * Type) +
#                        Error(subjID / (Load * Type))), contrasts = contr.sum())
# summary(RTaov)
# RTaov <- tidy(RTaov)
# 
# 
# 
# 
# data.long.summary <- summarySE(data.long, measurevar="ReactionTime", groupvars="Condition", na.rm = TRUE)

# ggplot(data.long.summary, aes(Condition, ReactionTime, fill = as.factor(Condition))) +
#   geom_bar(stat = "summary", fun.y = "mean", na.rm = TRUE) +
#   geom_errorbar(aes(ymin=ReactionTime-se, ymax=ReactionTime+se), width=.1)

@@

``` {r MAD, include = FALSE}
###  MAD analyses ###
results.long <- gather(data, key = "Condition", value = "MAD",
                       lo.emo.sur_MAD, hi.emo.sur_MAD, lo.neu.sur_MAD, hi.neu.sur_MAD)
results.long$load <- ifelse(results.long$Condition == "lo.emo.sur_MAD", "Low",
                            ifelse(results.long$Condition == "lo.neu.sur_MAD", "Low", "High"))
results.long$type <- ifelse(results.long$Condition == "lo.emo.sur_MAD", "Emo",
                            ifelse(results.long$Condition == "hi.emo.sur_MAD", "Emo", "Neu"))

@@

res.long.sum <- summarySE(results.long, measurevar="MAD", groupvars = "Condition")
```

``` {r MAD plot, include = TRUE}
ggplot(res.long.sum, aes(Condition, MAD, fill = as.factor(Condition))) +
  geom_bar(stat = "summary", fun.y = "mean") +
  geom_errorbar(aes(ymin=`MAD`-se, ymax=`MAD`+se), width=.1)
```
Finally, we assessed differences in maximum absolute deviation (MAD) across the WM trial conditions.

### 2019-08-07 Manuscript/Manuscript.tex
Updated manuscript, updated cleaning
Removing ridiculous variable creation in the cleaning script. Implementing "which" statements.

Manuscript runs, but is still messy.

To assses for normality, the data were first tested with Shapiro-Wilk's test. All conditions appeared to be sampled from normal distributions (p's \textgreater{} .08). A Load (Low, High) X Type (Neutral, Emotional) repeated measures ANOVA was used to assess differences in the RTs. There was a trend towards a main effect of type, F(1, 49) = 3.82, p = 0.06. However, follow up Wilcoxon signed rank tests did not reveal any differences that survived correction for multiple comparisons. There was a trend for RTs of face ratings on high load emotional trials to be longer than high load neutral trials (p =), and a similar pattern for low load emotional trial ratings to take longer than high load neutral trials (p = . One other comparison approached trend levels of signficance, with low load neutral trial ratings taking longer than high neutral loads, (p = . All other comparisons were non-significant (p's \textgreater{} .

@@

\begin{verbatim}
## 
##  Shapiro-Wilk normality test
## 
## data:  data$lo.neu.sur_n_RT
## W = 0.92168, p-value = 0.003408
\end{verbatim}

\begin{verbatim}
## 
##  Shapiro-Wilk normality test
## 
## data:  data$lo.neu.sur_p_RT
## W = 0.96281, p-value = 0.139
\end{verbatim}

\begin{verbatim}
## 
##  Shapiro-Wilk normality test
## 
## data:  data$hi.neu.sur_n_RT
## W = 0.9405, p-value = 0.01547
\end{verbatim}

\begin{verbatim}
## 
##  Shapiro-Wilk normality test
## 
## data:  data$hi.neu.sur_p_RT
## W = 0.98072, p-value = 0.6489
\end{verbatim}

\begin{verbatim}
## 
##  Shapiro-Wilk normality test
## 
## data:  data$lo.emo.sur_n_RT
## W = 0.94444, p-value = 0.02027
\end{verbatim}

\begin{verbatim}
## 
##  Shapiro-Wilk normality test
## 
## data:  data$lo.emo.sur_p_RT
## W = 0.90016, p-value = 0.002575
\end{verbatim}

\begin{verbatim}
## 
##  Shapiro-Wilk normality test
## 
## data:  data$hi.emo.sur_n_RT
## W = 0.95402, p-value = 0.05001
\end{verbatim}

\begin{verbatim}
## 
##  Shapiro-Wilk normality test
## 
## data:  data$hi.emo.sur_p_RT
## W = 0.88408, p-value = 0.002496
\end{verbatim}

\begin{verbatim}
## 
##  Wilcoxon signed rank test
## 
## data:  data$hi.neu.sur_n_RT and data$hi.neu.sur_p_RT
## V = 604, p-value = 0.2076
## alternative hypothesis: true location shift is not equal to 0
\end{verbatim}

\begin{verbatim}
## 
##  Wilcoxon signed rank test
## 
## data:  data$lo.emo.sur_n_RT and data$lo.emo.sur_p_RT
## V = 392, p-value = 0.7634
## alternative hypothesis: true location shift is not equal to 0
\end{verbatim}

\begin{verbatim}
## 
##  Wilcoxon signed rank test
## 
## data:  data$hi.emo.sur_n_RT and data$hi.emo.sur_p_RT
## V = 260, p-value = 0.9485
## alternative hypothesis: true location shift is not equal to 0
\end{verbatim}

\includegraphics{Manuscript_files/figure-latex/RT by ratings-1.pdf}
Next, we tested for reaciton time differences between positive and negative interpretations of surprised facial expressions within each working memory load condition. Given the non-normality of these data, we used paired-sample Wilcoxon signed rank tests for assessing differences between positive and negative ratings of surprise RTs. This difference was significant \emph{only} for the low emotional load trials, with surprise rated as positive taking signficantly longer than surprise rated as negative (.009). All other comparisons were not significant (p's \textgreater{} .200). Further, this effect survived Bonferroni correction (p = .012).

\begin{verbatim}
##              Df Sum Sq Mean Sq F value Pr(>F)  
## load          1  0.164 0.16398   5.118 0.0248 *
## type          1  0.002 0.00154   0.048 0.8265  
## load:type     1  0.087 0.08683   2.710 0.1013  
## Residuals   196  6.279 0.03204                 
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

>>>>

To assess for normality, the data were first tested with Shapiro-Wilk's test. Two conditions did not appear to be sampled from normal distributions, so non-parametric tests were used. Overall, there was a trending difference across the four conditions, \(\chi^{2}\)(3.00) = 7.15, p .067. Wilcoxon signed rank tests were used to assess post-hoc comparisons and Bonferroni corrected p-value = 0.01. While none of the post-hoc comparisons reached the adjusted significance level, there was a trending difference between emotional and neutral RTs in the high load condition, Z = 2.51, p = .012, such that high emotional WM loads had slower RTs. Two other comparisons were trending for traditional levels of significance. Low emotional WM loads tended to take marginally longer than high neutral WM loads, Z = 1.96, p = .050, and low neutral WM loads took marginally longer than high neutral WM laods, Z = -1.75, p = 0.08. All other comparisons were not significant.

@@

Next, we tested for reaciton time differences between positive and negative interpretations of surprised facial expressions within each working memory load condition. Given the non-normality of these data, we used paired-sample Wilcoxon signed rank tests for assessing differences between positive and negative ratings of surprise RTs. This difference was significant \emph{only} for the low emotional load trials, with surprise rated as positive taking signficantly longer than surprise rated as negative (.009). All other comparisons were not significant (p's \textgreater{} .200). Further, this effect survived Bonferroni correction (p = .012).

\begin{verbatim}
##              Df Sum Sq Mean Sq F value Pr(>F)  
## load          1  0.257 0.25709   4.599 0.0332 *
## type          1  0.002 0.00230   0.041 0.8394  
## load:type     1  0.001 0.00061   0.011 0.9170  
## Residuals   196 10.956 0.05590                 
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}
